Model for Porous Silicon Structures with a Lateral Gradient

### 2020-11-13 paper.tex
Adapt to Elsevier. Make small corrections.

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{showkeys}
%\usepackage{ieeetr}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

\title{Model for Porous Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}
\author[1,2]{V. Agarwal}
\author[2]{W. L. Mochán}

\affil[1]{Centro de
  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, México}
\begin{document}

@@

\begin{abstract}

A variety of optical devices and applications may be based on layered
systems which have a lateral gradient in both their refractive indices
and their thicknesses. They may be fabricated of porous silicon (PS) through an
electrochemical process in which the etching current depends on position. Thus, the possibility of
predicting the local current density $j$ and the corresponding
porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties through
ultraviolet-visible-near infrared reflectance
spectroscopy, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  The dependence of
porosity and thickness with position was corroborated through scanning electron microscopy. We
compared the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel non-homogenous devices with lateral gradients which can be used
for manifold applications.

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}

@@

We consider first a system made of identical {\em unit} charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential $\phi$ it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta^{(2)}(\bm r_\|-\bm
  R)\delta^{(1)}(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta^{(1)}(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane, $\{\bm G\}$ is the 2D
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta^{(1)}(z),
 \end{eqnarray}
for each coefficient, an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity (for $G\ne 0$), we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane, given by the
symmetric solution that decays exponentially as we get away, upwards
or downwards, from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

The morphology of the etched porous layers (plan-view and
cross-sectional) was observed using (SEM) scanning electron microscopy
(Hitachi SU1510  High Technologies Canada,  Inc., Toronto, Canada).

@@

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=1.2\textwidth]{j_Ivsxy.png}
  \includegraphics[width=\textwidth]{j_Ivsx.png}
  \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
    the surface of the sample through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
    the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
    point-like electrode at $\bm r_0=(0.2\,\text{cm},
    0.74\,\text{cm},0.9\,\text{cm})$ (top panel). Normalized current
    along the center line $y=0.74\,\text{cm}$ (bottom
    panel).}
  \label{fig:DR1}
\end{figure}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
that vary mostly along the $x$ direction. Of course, this would differ
for cells with different aspect ratios and for different positions of
the electrode.

\subsection{Samples }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $G_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate the centerline with a
    dashed line and eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the sealing o-ring.}
  \label{fig:SI3}
\end{figure}

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$G_3$
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to fail within that region and close to the border, at distances of the order of the radius
of the cross-section of the o-ring, of the order of a milimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n=x_n+w$ as the distance to the sealing o-ring,
where $x_n$ is the corresponding distance to the wall of the
cell.

@@

Using Eqs.  \eqref{Eq:ECMR}-\eqref{eq:v} we can calculate the
reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{jlr}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $G_1$, $G_2$ and
    $G_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as the results corresponding to sample $G_2$ in
Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
of the other samples, in order to facilitate the visualization of the
results, we artificially shifted horizontally towards the
right their contributions to Fig. \ref{fig:Rvsjl} by
$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
be grouped along bright and dark bands and that they correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and the minima are not as low.

The theoretical reflectance could as well be calculated using
\eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.

@@

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. VA acknowledges support from CONACyT Basic Sciences project
A-S1 30393 and from PRODEP, and is grateful to ICF where she spent a
sabatical. CAOD is grateful for a scholarship from CONACyT.
\bibliographystyle{unsrt}
\bibliography{bibligrin}
\end{document}

>>>>

\documentclass[review,sort&compress]{cas-sc}
%\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[numbers]{natbib}
%\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{showkeys}
%\usepackage{ieeetr}
\usepackage{bm}
\usepackage{hyperref}
%\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

\begin{document}
\shorttitle{Model for PS Structures with a Lateral Gradient}
\shortauthors{Ospina-Delacruz et al.}
\title[mode=title]{Model for Porous Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0000-0000-0000]
\ead{crisalod@gmail.com}
\credit{Investigation; Software; Writing - original draft}
\author[1,2]{V. Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Funding acquisition; Investigation; Supervision; Software; Writing - review \& editing}
\author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
%\cormark[1]
\ead{mochan@fis.unam.mx}
\credit{Conceptualization; Funding acquisition; Investigation;
  Methodology; Supervision; Writing - review \& editing}
\address[1]{Centro de
  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\address[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, México}
\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
%\cortext[cor1]{Corresponding author}

\begin{keywords}
  Porous Silicon\sep GRIN \sep Reflectance Spectra.
\end{keywords}

@@

\begin{abstract}
A variety of optical devices and applications may be based on layered
systems which have a lateral gradient in both their refractive indices
and their thicknesses. They may be fabricated of porous silicon (PS) through an
electrochemical process in which the etching current depends on position. Thus, the possibility of
predicting the local current density $j$ and the corresponding
porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties through
ultraviolet-visible-near infrared reflectance
spectroscopy, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  The dependence of
porosity and thickness with position was corroborated through scanning electron microscopy. We
compared the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel non-homogenous devices with lateral gradients which can be used
for manifold applications.
\end{abstract}

@@

We consider first a system made of identical {\em unit} charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential $\phi$ it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta^{(2)}(\bm r_\|-\bm
  R)\delta^{(1)}(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta^{(1)}(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane, $\{\bm G\}$ is the 2D
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the 2D Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta^{(1)}(z),
 \end{eqnarray}
for each coefficient, an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity (for $G\ne 0$), we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane, given by the
symmetric solution that decays exponentially as we get away, upwards
or downwards, from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

The morphology of the etched porous layers (plan-view and
cross-sectional) was observed with a {\em Hitachi SU1510} scanning electron microscope
(SEM).
%High Technologies Canada,  Inc., Toronto, Canada).

@@

\section{Discussion and Results}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{j_Ivsxy.png}
  \includegraphics[width=.6\textwidth]{j_Ivsx.png}
  \caption{Normalized current density $j_\perp(x,y,0)/I$ calculated a
    the surface of the sample through
    Eq. (\ref{Eq:J}) for a
    system as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
    the surface of the electrolyte at a heigth $c=1.0\,\text{cm}$, with a
    point-like electrode at $\bm r_0=(0.2\,\text{cm},
    0.74\,\text{cm},0.9\,\text{cm})$ (top panel). Normalized current
    along the center line $y=0.74\,\text{cm}$ (bottom
    panel).}
  \label{fig:DR1}
\end{figure}
In Fig. \ref{fig:DR1} we show the current density $j_\perp(x,y,0)$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
that vary mostly along the $x$ direction. Of course, this would differ
for cells with different aspect ratios and for different positions of
the electrode.

\subsection{Samples }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $G_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate the centerline with a
    dashed line and eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the left side sealing o-ring.}
  \label{fig:SI3}
\end{figure}

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$G_3$
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to {\em fail} within that region and close to the border, at distances of the order of the radius
of the cross-section of the o-ring, about a milimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n=x_n+w$ as the distance to the edge of
the etched sample, determined by the position of the sealing o-ring,
whereas $x_n$ is the corresponding distance to the wall of the
cell.

@@

Using Eqs.  \eqref{Eq:ECMR}-\eqref{eq:v} we can calculate the
reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{jlr}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $G_1$, $G_2$
    (shifted, see text) and  $G_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as the results corresponding to sample $G_2$ in
Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
of the other samples, in order to facilitate the visualization of the
results, we artificially shifted horizontally towards the
right their contributions to Fig. \ref{fig:Rvsjl} by
$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
be grouped along bright and dark bands and that they correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and the minima are not as low.

The theoretical reflectance could as well be calculated using Eqs.
\eqref{Eq:Brugg}-\eqref{eq:v} and a transfer matrix approach for more
complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.

@@

\section*{Acknowledgments}
\label{sec:acknowledgments}
CAOD is grateful for a scholarship from CONACyT and to
V. Castillo-Gallardo for useful discussions. VA acknowledges support
from CONACyT Basic Sciences project A-S1 30393 and from PRODEP, and is
grateful to ICF where she spent a sabatical.
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119.

\printcredits

\bibliographystyle{unsrt}
\bibliography{bibligrin}
\end{document}
